R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections

### 2022-03-30 MS_physiology_infection.Rmd
Add files via upload

##  Create Figure 2a
## -----------------------------------------------------------------------------
Fig_2A  <- ggplot(tab_cont) +  
  aes(Timepoint, Count, fill = Prevalence) +  
  facet_wrap(facets = "Treatment") +  
  geom_bar(stat = 'identity',  width = 0.3) +  
  labs(y = "Count of nestlings") +  
  geom_text(aes(label = Count),position  = position_stack(0.5)) +  
  scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) +  
  theme(axis.title.x  =  element_blank(), 
        strip.text = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16))

@@

## Figure 2b
## -----------------------------------------------------------------------------
Fig_2B = ggplot(mean_infint) +
  aes(Sampling_rank, Infection_intensity, group = Treatment) +
  geom_vline(xintercept  =  "First sampling", linetype = "dashed", color = 'darkgrey') +
  geom_vline(xintercept = "Second sampling", linetype = "dashed", color = 'darkgrey') +
  labs(y = "Mean infection intensity") +
  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) + 
  stat_summary(fun = mean, geom = "point",size = 5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
  scale_color_manual(values = c("lightgrey","black")) + 
  theme_classic() + 
  theme(axis.title.x = element_blank(),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16),
        plot.margin = unit(c(0,0,0,30), "pt"))

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <- Fig_2A + Fig_2B +
  plot_annotation(tag_levels = 'A') + 
  theme(plot.tag = element_text(size = 16, face = "bold"))

@@

## Effects on physiology

Exploring effects on physiology of nestlings due to the treatment:

No treatment effect on breathing rate

```{r}
## Table S1
## -----------------------------------------------------------------------------
lm_d1 = lm(Breathing_rate ~ Treatment, data = df)
summary(lm_d1)
```

No treatment effect on body temperature

```{r}
## Table S1
## -----------------------------------------------------------------------------
lm_d2 <- lm(body_temperature ~ Treatment, data = df)
summary(lm_d2)
```

No treatment effect on body condition change

```{r}
## Table S1
## -----------------------------------------------------------------------------
lm_d3 <- lm(delta_body_condition~Treatment, data = df)
summary(lm_d3)
```

No treatment effect on growth rates

```{r}
## Table S1
## -----------------------------------------------------------------------------
lm_d4 <- lm(Growth_rate~Treatment, data = df)
summary(lm_d4)

## Create Table S1
## -----------------------------------------------------------------------------
tab_model(
  lm_d1,lm_d2,lm_d3,lm_d4,
  show.reflvl = T,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  pred.labels = c("Intercept","Treatment [Malarone]"),
  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
  file = "./Tables/TableS1_Physiological_parameters_in_decreasing_control_treated.html")
```

@@

## Plotting predicted values across infection stages
## -----------------------------------------------------------------------------
Fig_4A <- ggplot(mod_br) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
  label = "n.s.", size = 5)
```

@@

# Plotting predicted values across infection stages
Fig_4B <- ggplot(mod_bt) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_errorbar(aes(ymin = mod_bt$conf.low,ymax = mod_bt$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt$predicted - mod_bt$std.error,ymax = mod_bt$predicted + mod_bt$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.y = element_text(size = 14, margin = unit(c(0,3,0,0),"mm")), 
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 40.6, xend = 4, yend = 40.6)) + 
    geom_text(aes(x = 2.5, y = 40.7),
              label = "n.s.", size = 5)
```

@@

Fig_4C = ggplot(mod_bc) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc$conf.low,ymax = mod_bc$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc$predicted - mod_bc$std.error,ymax = mod_bc$predicted + mod_bc$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bc$conf.high) + 17, xend = 4, yend = max(mod_bc$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, y = max(mod_bc$conf.high) + 23),
              label = "n.s.", size = 5)
```

@@

Fig_4D = ggplot(mod_gr) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr$conf.low,ymax = mod_gr$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr$predicted - mod_gr$std.error,ymax = mod_gr$predicted + mod_gr$std.error), 
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 14, margin = unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 30, "pt"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_gr$conf.high) + 1.2, xend = 4, yend = max(mod_gr$conf.high) + 1.2)) + 
    geom_text(aes(x = 2.5, y = max(mod_gr$conf.high) + 2),
              label = "n.s.", size = 5)
```

## Summarise models

@@

```{r}
## Figure 4 
## -----------------------------------------------------------------------------
fig4 <- Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig4

ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)

# Table 3
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table3_results_lmer_physiological_parameters_p.val_kr.html")
```

@@

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_5A = ggplot(mod_br_para) + 
  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_errorbar(aes(ymin = mod_br_para$lower_CI,
                    ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, 
                    ymax = mod_br_para$predicted + mod_br_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
                              xend = 5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
              label = "n.s.", size = 6)
```

@@

## Obtain sample sizes for labels 
## ----------------------------------------------------------------------------- 
m2 = table(df$Infection_intensity.2[!is.na(df$body_temperature)])

## Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_5B = ggplot(mod_bt_para) + 
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
                size = 8,colour = wes_palette("Zissou1",5), width = 0,) + 
  labs(x = "", y = "Body temperature") + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
  geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.3),
            label = "P = 0.006", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                   xend = 1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.1)) + 
  geom_segment(size = .8,
               aes(x = 5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.1,
                   xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
```

@@

Fig_5C = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
                colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted - mod_bc_para$se,
                    ymax = mod_bc_para$predicted + mod_bc_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),  
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "P = 0.080", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

@@

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_5D = ggplot(mod_gr_para) + 
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
                    ymax = mod_gr_para$higher_CI), colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr_para$predicted - mod_gr_para$se,
                    ymax = mod_gr_para$predicted + mod_gr_para$se),size = 8, 
                colour = wes_palette("Zissou1",5), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
               aes(x = 1, y = 30, xend = 5, yend = 30)) + 
  geom_text(aes(x = 3, y = 31),
            label = "P = 0.094", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = 29, xend = 1, yend = 30)) + 
  geom_segment(size = .8,
               aes(x = 5, y = 29, xend = 5, yend = 30))
```

@@

```{r summary}
## Create multipanel Figure 5
## -----------------------------------------------------------------------------
fig5 = Fig_5A + Fig_5B + Fig_5C + Fig_5D + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig5

ggsave(fig5,filename = "./Figs/Fig5_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

## Table 4 
## ----------------------------------------------------------------------------- 
sjPlot::tab_model(
  lmer_br_para,
  lmer_bt_para,
  lmer_bc_para,
  lmer_gr_para,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  p.val = "kr",
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table4_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
```

>>>>

##  Create Figure 2a
## -----------------------------------------------------------------------------
Fig_2A  <- ggplot(tab_cont) +  
  aes(Timepoint, Count, fill = Prevalence) +  
  facet_wrap(facets = "Treatment") +  
  geom_bar(stat = 'identity',  width = 0.3) +  
  labs(y = "Count of nestlings") +  
  geom_text(aes(label = Count),position  = position_stack(0.5),size=5) +  
  scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) + 
  scale_x_discrete(labels = c("First\nsampling","Second\nsampling","First\nsampling","Second\nsampling"))+  
  theme(axis.title.x  =  element_blank(), 
        strip.text = element_text(size = 22, face = "bold"),
        legend.text = element_text(size = 20),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.90),
        axis.title.y = element_text(size = 28, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text.x = element_text(size = 22, margin =  unit(c(3, 0, 0, 0), "mm")),
        axis.text.y = element_text(size = 22, margin =  unit(c(0, 1, 0, 0), "mm")))

@@

## Figure 2b
## -----------------------------------------------------------------------------
Fig_2B <- ggplot(mean_infint) +
  aes(Sampling_rank, Infection_intensity, group = Treatment) +
  geom_vline(xintercept  =  "First sampling", linetype = "dashed", color = 'darkgrey') +
  geom_vline(xintercept = "Second sampling", linetype = "dashed", color = 'darkgrey') +
  labs(y = "Mean infection intensity") +
  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) + 
  scale_x_discrete(labels = c("First\nsampling","Second\nsampling"))+
  stat_summary(fun = mean, geom = "point",size = 5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
  scale_color_manual(values = c("lightgrey","black")) + 
  theme(axis.title.x = element_blank(),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 22),
        axis.title.y = element_text(size = 28, margin =  unit(c(0, 5, 0, 0), "mm")),
        axis.text.x = element_text(size = 22, margin =  unit(c(3, 0, 0, 0), "mm")),
        axis.text.y = element_text(size = 22, margin =  unit(c(0, 1, 0, 3), "mm")),
        plot.margin = unit(c(0,0,0,30), "pt"))

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <-  Fig_2A +Fig_2B+
  plot_annotation(tag_levels = 'a') + 
  theme(plot.tag = element_text(size = 22, face = "bold"))

@@

@@

## Plotting predicted values across infection stages
## -----------------------------------------------------------------------------
Fig_S1A <- ggplot(mod_br) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
  label = "n.s.", size = 5)
```

@@

# Plotting predicted values across infection stages
Fig_S1B <- ggplot(mod_bt) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_errorbar(aes(ymin = mod_bt$conf.low,ymax = mod_bt$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt$predicted - mod_bt$std.error,ymax = mod_bt$predicted + mod_bt$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.y = element_text(size = 18, margin = unit(c(0,3,0,0),"mm")), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 40.6, xend = 4, yend = 40.6)) + 
    geom_text(aes(x = 2.5, y = 40.7),
              label = "n.s.", size = 5)
```

@@

Fig_S1C = ggplot(mod_bc) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc$conf.low,ymax = mod_bc$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc$predicted - mod_bc$std.error,ymax = mod_bc$predicted + mod_bc$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bc$conf.high) + 17, xend = 4, yend = max(mod_bc$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, y = max(mod_bc$conf.high) + 23),
              label = "n.s.", size = 5)
```

@@

Fig_S1D = ggplot(mod_gr) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr$conf.low,ymax = mod_gr$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr$predicted - mod_gr$std.error,ymax = mod_gr$predicted + mod_gr$std.error), 
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 18, margin = unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 30, "pt"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_gr$conf.high) + 1.2, xend = 4, yend = max(mod_gr$conf.high) + 1.2)) + 
    geom_text(aes(x = 2.5, y = max(mod_gr$conf.high) + 2),
              label = "n.s.", size = 5)
```

## Summary four models

@@

```{r}

# Table 1 and Table S3 
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  show.df=T,
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr.html")
```

@@

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4A = ggplot(mod_br_para) + 
  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_errorbar(aes(ymin = mod_br_para$lower_CI,
                    ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, 
                    ymax = mod_br_para$predicted + mod_br_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
                              xend = 5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
              label = "n.s.", size = 6)
```

@@

## Obtain sample sizes for labels 
## ----------------------------------------------------------------------------- 
m2 = table(df$Infection_intensity.2[!is.na(df$body_temperature)])
mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m2)), levels = c(paste0(x,"\nn= ",m2))))

## Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4B = ggplot(mod_bt_para) + 
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
                size = 8,colour = wes_palette("Zissou1",5), width = 0,) + 
  labs(x = "", y = "Body temperature") + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
  geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.3),
            label = "P = 0.006", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                   xend = 1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.1)) + 
  geom_segment(size = .8,
               aes(x = 5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.1,
                   xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
```

@@

Fig_4C = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
                colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted - mod_bc_para$se,
                    ymax = mod_bc_para$predicted + mod_bc_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),  
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "P = 0.080", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

@@

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4D = ggplot(mod_gr_para) + 
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
                    ymax = mod_gr_para$higher_CI), colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr_para$predicted - mod_gr_para$se,
                    ymax = mod_gr_para$predicted + mod_gr_para$se),size = 8, 
                colour = wes_palette("Zissou1",5), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
               aes(x = 1, y = 30, xend = 5, yend = 30)) + 
  geom_text(aes(x = 3, y = 31),
            label = "P = 0.094", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = 29, xend = 1, yend = 30)) + 
  geom_segment(size = .8,
               aes(x = 5, y = 29, xend = 5, yend = 30))
```

@@

```{r summary}
## Create multipanel Figure 4
## -----------------------------------------------------------------------------
fig4 = Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig4

ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

## Table 4 
## ----------------------------------------------------------------------------- 
sjPlot::tab_model(
  lmer_br_para,
  lmer_bt_para,
  lmer_bc_para,
  lmer_gr_para,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  p.val = "kr",
  show.df = T,
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table4_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
```
